Illusion Game Validation (Study 2)

### 2022-09-05 study2/study2.Rmd
update

plot_ppcheck(model_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_zollner_rt)
# performance::check_model(model_zollner_rt)
# parameters::parameters(model)

@@

plot_ppcheck(model_white_rt)
# performance::check_model(model_white_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_mullerlyer_rt)
# performance::check_model(model_mullerlyer_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_ponzo_rt)
# performance::check_model(model_ponzo_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_poggendorff_rt)
# performance::check_model(model_poggendorff_rt)
# parameters::parameters(model)
```

@@

rez <- parameters::n_factors(data, n_max=15)
plot(rez)

@@

anova(m0, m1, m1b, m2)

@@

>>>>

plot_ppcheck(model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
# performance::check_model(model_verticalhorizontal_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_zollner_rt, gam_zollner_rt)
# performance::check_model(model_zollner_rt)
# parameters::parameters(model)

@@

plot_ppcheck(model_white_rt, gam_white_rt)
# performance::check_model(model_white_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_mullerlyer_rt, gam_mullerlyer_rt)
# performance::check_model(model_mullerlyer_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_ponzo_rt, gam_ponzo_rt)
# performance::check_model(model_ponzo_rt)
# parameters::parameters(model)
```

@@

plot_ppcheck(model_poggendorff_rt, gam_poggendorff_rt)
# performance::check_model(model_poggendorff_rt)
# parameters::parameters(model)
```

@@

rez <- parameters::n_factors(data, n_max=15)
rez
plot(rez)

@@

# Model 4 - No middle level
lvl1 <- paste("i =~", data$Name)

m4 <- sem(model = paste0(c(lvl1), collapse = "\n"),
          data  = random,
          bounds = "standard",
          estimator = "ML"
          )

anova(m0, m1, m1b, m2, m4)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
# Variance Explained
SumCy <- sum(cov(random[-1]), na.rm = TRUE)

get_r2 <- function(data, dat, SumCy) {
  Cx <- cov(data)
  Cxy <- cov(data, dat)
  solved <- tryCatch(solve(Cx), error = function(e) NULL)
  if (is.null(solved)) {
    return(NA)
    next
  } else {
    VAF <- t(Cxy) %*% solved %*% Cxy
    return(sum(VAF, na.rm = TRUE) / SumCy)
  }
}
var <- get_r2(data=dfsem["i"], dat=random[-1], SumCy)
```

Factor *i* explained `r insight::format_percent(var)` of the variance of the dataset.
